\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-20 latex/article_vol2.tex
Fixed typo

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its
  variables. The results can be presented in an auto-generated,
  non-technical, stand-alone overview document, intended to be perused
  by an investigator with an understanding of the variables in the
  data and the experimental design, but not necessarily knowledge of
  \R{R}. Thereby, \R{cleanR} aids the dialogue between data analysist
  and field experts, while also providing easy documentation of data
  cleaning steps and data quality control. Moreover, the \R{cleanR}
  solution changes the data cleaning process from the usual ad hoc
  approach to a systematic, well-documented endeavor.  \R{cleanR} also
  provides a suite of more typical \R{R} tools for interactive data
  quality assessment and -cleaning. \hl{Hvad menes der/henvises der
    til  med denne sætning?}

>>>>

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its
  variables. The results can be presented in an auto-generated,
  non-technical, stand-alone overview document, intended to be perused
  by an investigator with an understanding of the variables in the
  data and the experimental design, but not necessarily knowledge of
  \R{R}. Thereby, \R{cleanR} aids the dialogue between data analysists
  and field experts, while also providing easy documentation of data
  cleaning steps and data quality control. Moreover, the \R{cleanR}
  solution changes the data cleaning process from the usual ad hoc
  approach to a systematic, well-documented endeavor.  \R{cleanR} also
  provides a suite of more typical \R{R} tools for interactive data
  quality assessment and -cleaning. \hl{Hvad menes der/henvises der
    til  med denne sætning?}
